\section{Data and Reproducibility Statement}
\label{sec:data-reproducibility}

The evaluation suite is designed to be reproducible from archived inputs, fixed random seeds, documented simulator settings, and reported result tables. Archived CelesTrak and SatNOGS snapshots replace live API queries, so replay scenarios are not affected by later public-service changes. The public precise-reference probes use real ILRS satellite-laser-ranging normal points for LAGEOS-1 and LAGEOS-2 together with independent ILRS NSGF SP3-c products as bounded stress/provenance evidence. On the four-arc range-residual slice (384 normal points, 117 held out; deterministic temporal split), pooled held-out laser ranges are best fit by classical range-only weighted least squares, while both a learned bounded residual correction and a weighted-least-squares-plus-learned hybrid fail to generalise. The SP3 state-scored probes include strict held-out negatives for DBAR and the learned calibrator. These probes reduce external measurement-pipeline risk only; they do not validate the main simulator learned-versus-classical conclusion or operational POD. The multi-revolution SGP4-reference benchmark observes five real LEO objects through the study's real eight-station ground geometry over twelve-hour arcs and scores held-out reference-state position RMSE on a deterministic earlier-fit / later-held-out split; the fixed-noise UKF is best (1809.54~m), the hard-bounded learned residual correction is worse (2755.43~m), and SGP4 is an analytic mean-element propagation so magnitudes are a bounded model-mismatch stress, not operational accuracy. Synthetic nominal and stress splits use fixed orbit, force-model, visibility, and measurement-noise settings, and all methods are evaluated over a common scoring horizon.

The submission includes a versioned supplementary evidence package that provides a manifest, per-artifact SHA-256 checksums, a claim-to-record map, regeneration tiers, fixed data-generation settings, the $K=32$ endpoint replication records, the stress-only $K=96$ floor-power-scale replication record, the 15-seed cohort (seeds 41--55), trained-model records, validation criteria, evaluation audit records, and the complete learned-estimator architecture and training-objective specification of the manuscript appendix. The exact confidential access mechanism, artefact count, digest coverage, citation metadata date, reuse terms, and accepted-version archive condition are stated once in the Data availability statement. The paper itself reports the scientific protocol, result tables, figures, and claim boundaries needed to interpret the results.

The minimum table-regeneration tier verifies package integrity and regenerates the displayed result tables from recorded outputs, checking the reported numerics without retraining learned estimators. Reproduction of the full study requires regenerating the benchmark data, training the learned estimators under the stated curriculum and seeds, evaluating all classical and learned methods on the nominal, stress, and replay scenarios, regenerating the displayed figures and tables, and confirming that the rendered manuscript resolves citations. These steps are a full experiment rerun, not a formatting or submission check. The minimum tier is a short integrity/regeneration check; the full rerun/retraining tier can require many hours to days depending on parallelism.

The central quantitative claims remain bounded to the reported benchmark settings: the $K=32$ frozen-rule observed-step replication gives no learned positive against the per-scenario best classical reference, and the stress-only $K=96$ replication exceeds the prior floor-power design check while preserving the stress-row negative; the 15-seed records show directional stress gains over fixed-noise UKF for selected learned residual variants but no gain over tuned AUKF; a controlled force-model mismatch split finds the causal EKF best and no learned residual model beats it; a force-model mismatch mechanism diagnostic reproduces the adaptive-filter estimate exactly; an implemented KalmanNet-style learned-gain comparator never beats the tuned AUKF; the public ILRS/SP3 precise-reference probes return held-out DBAR and learned-calibrator negatives; a multi-revolution SGP4-reference benchmark has classical filters best; and graph-utility controls are mixed. The findings do not establish flight readiness, universal robustness, graph-causal superiority, operational POD, or a stability-prediction task result.
